\documentclass[letterpaper, 10pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=0.75in]{geometry}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{parskip}
\usepackage{hyperref}

% Custom commands for section headers and colored text
\newcommand{\resumeSection}[1]{\section*{\textcolor{blue}{\large #1}}}
\newcommand{\resumeSubSection}[1]{\subsection*{#1}}
\newcommand{\resumeSubSubSection}[1]{\hspace{12pt}\textit{#1}}
\newcommand{\resumeItem}[2]{\item \textbf{#1}: #2}
\newcommand{\resumeSubItem}[1]{\hspace{12pt}\textbullet\hspace{6pt}#1}

% Name and contact information
\newcommand{\Name}{Your Name}
\newcommand{\Email}{youremail@example.com}
\newcommand{\Phone}{(123) 456-7890}
\newcommand{\LinkedIn}{\href{https://www.linkedin.com/in/your-profile}{LinkedIn Profile}}
\newcommand{\GitHub}{\href{https://github.com/yourusername}{GitHub Profile}}

\begin{document}

% Header
\begin{center}
    \textbf{\Huge \Name}\\
    \vspace{4pt}
    \small \Email \hspace{10pt} \textbullet \hspace{10pt} \Phone \hspace{10pt} \textbullet \hspace{10pt} \LinkedIn \hspace{10pt} \textbullet \hspace{10pt} \GitHub
\end{center}

% Education section
\resumeSection{Education}
\begin{itemize}[leftmargin=*, label={}]
    \resumeItem{University Name}{Bachelor of Science in Computer Science \hfill \textit{Expected Graduation: May 2024}}
    \resumeSubItem{Relevant Coursework: Data Structures, Algorithms, Web Development, Database Systems}
\end{itemize}

% Projects section
\resumeSection{Projects}
\begin{itemize}[leftmargin=*]
    \resumeItem{Project 1}{A description of Project 1 and its key features. Technologies used: XYZ.}
    \resumeItem{Project 2}{A description of Project 2 and its key features. Technologies used: ABC.}
\end{itemize}

% Skills section
\resumeSection{Skills}
\begin{itemize}[leftmargin=*]
    \resumeItem{Programming Languages}{Python, Java, JavaScript}
    \resumeItem{Web Development}{HTML, CSS, React}
    \resumeItem{Database}{SQL, MongoDB}
\end{itemize}

% Extracurricular section
\resumeSection{Extracurricular Activities}
\begin{itemize}[leftmargin=*]
    \resumeItem{Club Name}{Description of your involvement and any leadership positions.}
    \resumeItem{Volunteer Work}{Description of your volunteer activities and their impact.}
\end{itemize}

% Awards section
\resumeSection{Awards and Honors}
\begin{itemize}[leftmargin=*]
    \resumeItem{Scholarship Name}{Description of the scholarship and your achievement.}
    \resumeItem{Award Name}{Description of the award and the recognition received.}
\end{itemize}

% Footer
\begin{center}
    \footnotesize Last updated: \today
\end{center}

\end{document}

